\section*{Peer-reviewed publications}

\begin{itemize}
	\item Xinzhe Wu and Serge G. Petiton, ”A Distributed and Parallel Asynchronous Unite and Conquer Method to Solve Large Scale Non-Hermitian Linear Systems” in HPC Asia 2018: International Conference on High Performance Computing in Asia-Pacific Region, Tokyo, Japan. 
	\item Xinzhe Wu, Serge G. Petiton and Yutong Lu, ”A Parallel Generator of Non-Hermitian Matrices computed from Given Spectra” in VECPAR 2018: 13th International Meeting on High Performance Computing for Computational Science, S\~ao Pedro, Brazil.
	\item Xinzhe Wu and Serge G. Petiton, ”A Distributed and Parallel Unite and Conquer Method to Solve Sequences of Non-Hermitian Linear Systems”. Submitted to Japan Journal of Industrial and Applied Mathematics. [Under Review].
	\item Xinzhe Wu and Serge G. Petiton, ”A Distributed and Parallel Asynchronous Unite and Conquer Method to Solve Large Scale Non-Hermitian Linear Systems with Multiple Right-hand Sides”. Submitted to Parallel Computing. [Submitted].
	\item Xinzhe Wu and Serge G. Petiton, ”Distributed Parallel Multi-level Programming Paradigm for Iterative Methods on Large-scale Clusters”. Submitted to CCGrid2019: 19th Annual IEEE/ACM International Symposium in Cluster, Cloud, and Grid Computing. [Submitted].
\end{itemize}

\section*{Invited and Contributed Talks}

\begin{itemize}
	\item Serge G. Petiton and Xinzhe Wu, ”An Asynchronous Distributed and Parallel Unite and Conquer Method to Solve Sequences of Non-Hermitian Linear systems” in MATHIAS 2018: Computational Science Engineering \& Data Science by TOTAL, Serris, France. 
	\item Xinzhe Wu, Serge G. Petiton and Yutong Lu, ”A Parallel Generator of Non-Hermitian Matrices Computed from Given Spectra” in VECPAR 18: 13th International Meeting on High Performance Computing for Computational Science, S\~ao Pedro, Brazil.
	\item Xinzhe Wu and Serge G. Petiton, ”A Parallel Generator of Non-Hermitian Matrices Computed from Given Spectra” in PMAA18: 10th International Workshop on Parallel Matrix Algorithms and Applications, Zurich, Switzerland.
	\item Xinzhe Wu and Serge G. Petiton, ”A Parallel Generator of Non-Hermitian Matrices Computed from Known Given Spectra” in 3rd Workshop on Parallel Programming Models - Productivity and Applications, Aachen, Germany.
	\item Xinzhe Wu and Serge G. Petiton, ”A Parallel Generator of Non-Hermitian Matrices Computed from Known Given Spectra” in SIAM PP18: SIAM Conference on Parallel Processing for Scientific Computing, Tokyo, Japan.
	\item  Serge G. Petiton and Xinzhe Wu, ”The Unite and Conquer GMRES-LS/ERAM method to solve sequences of Linear Systems” in EPASA 2018: International Workshop on Eigenvalue Problems: Algorithms, Software and Applications, in Petascale Computing, Tsukuba, Japan.
	\item Xinzhe Wu and Serge G. Petiton, ”A Distributed and Parallel Asynchronous Unite and Conquer Method to Solve Large Scale Non-Hermitian Linear Systems” in HPC Asia 2017: International Conference on High Performance Computing in Asia-Pacific Region, Tokyo, Japan.
	\item Serge G. Petiton, Xinzhe Wu and Tao Chang, ”A Distributed and Parallel Asynchronous Unite and Conquer Method to Solve Large Scale Non-Hermitian Linear Systems” in Preconditioning 2017: International Conference On Preconditioning Techniques For Scientific And Industrial Applications, Vancouver, Canada.
\end{itemize}

\section*{Posters}
\begin{itemize}
	\item Xinzhe Wu and Serge G. Petiton, ”Large Non-Hermitian Matrix Generation with Given Spectra” in EPASA 2018: International Workshop on Eigenvalue Problems: Algorithms, Software and Applications, in Petascale Computing, Tsukuba, Japan.
\end{itemize}

\section*{Software Manual/Technical Reports}
\begin{itemize}
	\item Xinzhe Wu, ”SMG2S Manual” in Maison de la Simulation, France - Version 1.0, 2018. 
\end{itemize}
\clearemptydoublepage