\documentclass{xinzhewu}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage[intoc, english]{nomencl}
\usepackage{enumerate}
\usepackage{multirow}
 \usepackage{enumitem} 
 \usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage[scientific-notation=true]{siunitx}
\usepackage{algpseudocode}
\usepackage{svg}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{nopageno}
\usepackage{color}
\usepackage{amsmath}
\usepackage{empheq}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{siunitx}
\usepackage{xcolor,colortbl}
\usepackage{array}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{ulem}
\usepackage{smartdiagram}
\usepackage{easybmat}
\usepackage{graphicx}
%\usepackage[numbers]{natbib}
\usepackage{dirtree} % for directory structure.
\usepackage{diagbox} 
%\usepackage[Glenn]{fncychap}  %chapter styles
\usepackage{mathtools}

\usepackage{amssymb}

\usepackage{textpos}

\usepackage{csquotes}

\usepackage{algorithm, float}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

\usepackage{xcolor}
\usepackage{enumerate}
\usepackage[scientific-notation=true]{siunitx}
\usepackage[misc]{ifsym}
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{amsmath}

\usepackage{easybmat}

\usepackage{minitoc} %List sections of chapter at beginning of that chapter

% Create a new environment for breaking code listings across pages.
\newenvironment{longlisting}{\captionsetup{type=listing}}{}


\newcolumntype{x}[1]{>{\centering\arraybackslash\hspace{0pt}}p{#1}}
\usepackage{makecell}

\usepackage{CJKutf8}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

\makeatletter
\newcommand*\bigcdot{\mathpalette\bigcdot@{.5}}
\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\makeatother

\usepackage{rotating}

\usepackage{minted}

\usepackage[square,numbers]{natbib}
%\bibliographystyle{dinat}
\bibliographystyle{plainnat}

\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}


\definecolor{maroon}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}

\lstdefinelanguage{XML}
{
	basicstyle=\ttfamily,
	morestring=[s]{"}{"},
	morecomment=[s]{?}{?},
	morecomment=[s]{!--}{--},
	commentstyle=\color{darkgreen},
	moredelim=[s][\color{black}]{>}{<},
	moredelim=[s][\color{red}]{\ }{=},
	stringstyle=\color{blue},
	identifierstyle=\color{maroon}
}

\lstset{language=C++,
	basicstyle=\ttfamily,
	keywordstyle=\color{blue}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	commentstyle=\color{green}\ttfamily,
	morecomment=[l][\color{magenta}]{\#}
}

%\renewcommand{\baselinestretch}{1.4}  % distance between two lines

\newenvironment{dedication}
{\clearpage           % we want a new page
	\thispagestyle{empty}% no header and footer
	\vspace*{\stretch{1}}% some space at the top 
	\itshape             % the text is in italics
	\raggedleft          % flush to the right margin
}
{\par % end the paragraph
	\vspace{\stretch{3}} % space at bottom is three times that at the top
	\clearpage           % finish off the page
}


\setcounter{tocdepth}{2}

\newcolumntype{x}[1]{>{\centering\arraybackslash\hspace{0pt}}p{#1}}

%\usepackage[UTF8]{ctex}
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={blue}} 

\makeatletter
\newenvironment{breakablealgorithm}
{% \\makeatletter begin{breakablealgorithm}
	\begin{center}
		\refstepcounter{algorithm}% New algorithm
		\hrule height.8pt depth0pt \kern2pt% \@fs@pre for \@fs@ruled
		\renewcommand{\caption}[2][\relax]{% Make a new \caption
			{\raggedright\textbf{\ALG@name~\thealgorithm} ##2\par}%
			\ifx\relax##1\relax % #1 is \relax
			\addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}%
			\else % #1 is not \relax
			\addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}%
			\fi
			\kern2pt\hrule\kern2pt
		}
	}{% \end{breakablealgorithm}
		\kern2pt\hrule\relax% \@fs@post for \@fs@ruled
	\end{center}
}
\makeatother


%
\makenomenclature
\renewcommand{\nomname}{List of Symbols}
\renewcommand{\nompreamble}{The next list describes several symbols that will be later used within the body of the document}

\title{\Large \textrm{Contribution \`a l’\'emergence de nouvelles m\'ethodes parall\`eles et reparties intelligentes utilisant un paradigme de programmation multi-niveaux pour le calcul extr\^eme}}

%\lesoustitre{Le sous titre est facultatif}

\discipline{Informatique}

\dirdethese{Serge G. Petiton}
\titredudirdethese{Universit\'e de Lille}

\jury{
	
\begin{tabular}{>{\normalsize}l>{\normalsize}l>{\small}l}
	&& \\
	Rapporteurs &  Michel Dayd\'e &- Directeur de l'IRT de Toulouse\\
	 &   &- Professeur \`a l'ENSEEIHT\\
	 &Michael A. Heroux &- Chercheur au Laboratoires National de Sandia \\
	Examinateurs & Yutong Lu &- Directrice de NSCC-Guangzhou \\
	&&- Professeur \`a l'Universit\'e de  Sun Yat-Sen\\
 	& Barbara Chapman  &-  Professeur \`a l'Universit\'e de Stony Brook\\
 	& &-  Chercheur au Laboratoires National de Brookhaven\\
 	&France Boillod-Cerneux& - Chercheur au CEA Saclay \\
	 & \textcolor{red}{A German ?} &-   \\
	Directeur & Serge G. Petiton &- Professeur \`a l'Universit\'e de Lille \\
\end{tabular}

}

\author{M. Xinzhe WU}

\date{Saclay, le 22 Mars 2019}

\nomdeuniversite{\textbf{\textrm{Universit\'e de Lille}}}
\logouniversite{logo_univ} %nom du fichier
\scalelogouniversite{0.2} % mise a l'echelle de l'image (0.5=50% par exemple)
\logolabo{logo_labo}
\scalelogolabo{0.2}

%\unite{Département d'histoire de la typographie}
\ecoledoc{\large École doctorale Sciences Pour l'Ing\'enieur Universit\'e Lille Nord-de-France}

\usepackage{nomencl}
\makenomenclature

\begin{document}

\maketitle
 
\clearemptydoublepage
\begin{dedication}
	\normalsize
	%This thesis is dedicated to my grandmother. Hope you can hear in the heaven.
	
	\vspace{0.2in}
	\begin{CJK*}{UTF8}{bsmi}
		{\CJKfamily{bkai}
			\large
			謹以此文獻給我的祖母劉占仙（1928-2015）}
	\end{CJK*}

\iffalse
\begin{textblock*}{\textwidth}(6cm,4cm)
	
	\begin{CJK*}{UTF8}{bsmi}
		\centerline{{\CJKfamily{bkai}戊戌年 $\bigcdot$小寒}}
		\centerline{{\CJKfamily{bkai}巴黎城}}
		\centerline{{\CJKfamily{bkai}歡鵲壘新巢}}
	\end{CJK*}
\end{textblock*}
\fi

\end{dedication}

\clearemptydoublepage

\chapter*{Acknowledgement}
\thispagestyle{empty}

First and foremost I would like to express my gratitude to my advisor of the thesis, Prof. Serge G. Petiton, for the continuous support of my Ph.D study and related research, for his patience, motivation, and immense knowledge. He enlightens me in the field of parallel computing and numerical algorithms. Also, he teaches me in how to do academic research during the three years. I am grateful for his wise guidance and inclusiveness throughout my three years' study. I benefited enormously from him about how to do the research and communicate it in an effective way. I feel so lucky to work under his supervision.

I warmly thank Michel Dayd\'e, Professor at ENSEEIHT, and Micheal Heroux, senior scientist at Sandia National Laboratory, who have done me the honor of being the reporters of my thesis. Thank you for your recommendations and your help.

My sincere thanks also goes to the MYX project and CNRS for funding my thesis. I am grateful for the warm welcome shown by the Maison de la Simulation, especially Edouard Audit, for accepting me to study at this laboratory and funding me for several international conferences. I would also thank Val\'erie Belle and all secretary members for helping me with numerous administrative work. I thank all the people I met during these three years for the pleasant atmosphere they were able to install. 

I have been privileged to visit with National Supercomputing Center in Guangzhou. I would like to thank them, especially Prof. Yutong Lu for sharing their knowledge and I have benefited from the fruitful discussion with them.

I would like to thank ROMEO HPC Center, Universit\'e de Reims Champagne-Ardenne. They provide me the access to their supercomputer ROMEO (both 2013 and 2018 versions), which are the major platforms for the experimentation within my dissertation. I appreciate Dr. Arnaud RENARD and his engnieering team for their technique supports.

Special thanks to my lovely friends in Paris for their help and encouragement. I am very thankful to have these friends who enrich my life with great happiness. It is hard to forget the days of drinking Chinese liquor together, which really eased my homesickness.

I also want to thank those who are dear to me. Their attentions and encouragements have accompanied me throughout this journey. I thank my parents for their support and unfailing confidence. Words cannot express how grateful I am to my mother and father for all of the sacrifices that you’ve made on my behalf. Thanks to my sister Kunze for being present at every moment.
	
At the end of this journey, I thank Yuxin for being able to accompany me in the best way and to continue to inspire me daily.


\clearemptydoublepage

\chapter*{Abstract}
\thispagestyle{empty}

\nomenclature{CPU}{Central Processing Unit}

\iffalse
An important application of supercomputers is to solve large-scale linear systems and eigenvalue problems by iterative methods. As the number of cores and heterogeneity of supercomputers increases, time spent in communication will be important comparing with the computation time, hence applications can be seen as a combination of distributed and parallel computing. Effectively solving these problems by iterative methods on large-scale platforms requires multi-levels of parallelism, and can minimize global communication, reduce synchronization, and facilitate asynchronous communication. In this thesis, we develop a distributed and parallel multi-level programming paradigm for iterative methods on High-Performance Computing (HPC) clusters. An implementation of a manager engine and runtime can handle the traffic, fault tolerance, and reusability of this paradigm on homogeneous and heterogeneous clusters. Finally, an example of iterative methods is developed based on this paradigm to simultaneously solve linear systems with multiple Right-hand sides (RHSs). Experiments on supercomputers have demonstrated that the implementation achieves better numerical and parallel performance than conventional methods.
\fi

\clearemptydoublepage

\selectlanguage{english}

\clearemptydoublepage

\frontmatter

{\tableofcontents}

{
\listoffigures
\addcontentsline{toc}{chapter}{\listfigurename}
}

{
\listoftables
\addcontentsline{toc}{chapter}{\listtablename}
}

{
\listofalgorithms
\addcontentsline{toc}{chapter}{\listalgorithmname}
}

\printnomenclature

%\listoflistings


\mainmatter % Ne pas oublier, avec \frontmatter et \backmatter

\chapter{Introduction}

%\addcontentsline{toc}{chapter}{Introduction}
\input{Introduction}

\chapter{State-of-the-art in High-Performance Computing} \label{State-of-the-art in High-Performance Computing}

\input{Chapter2}

\chapter{Krylov Subspace Methods}\label{Krylov Subspace Methods}

\input{Chapter3}

\chapter{Sparse Matrix Generator with Given Spectra}\label{Sparse Matrix Generator with Given Spectra}

\input{Chapter4}

\chapter[Unite and Conquer GMRES/LS-ERAM Method (UCGLE)]{Unite and Conquer GMRES/LS-ERAM Method (UCGLE)}\label{Unite and Conquer GMRES/LS-ERAM Method}

\input{Chapter5}

\chapter{UCGLE for Linear Systems with Sequences of Right-hand-sides}\label{UCGLE for Linear Systems with Sequences of Right-hand-sides}

\input{Chapter6}

\chapter{UCGLE for Linear Systems with Multiple Right-hand-sides} \label{UCGLE for Linear Systems with Multiple Right-hand-sides}

\input{Chapter7}

\chapter{Parameters Autotuning}  \label{Parameters Autotuning}

\input{Chapter8}

\chapter{YML Programming Paradigm for Unite and Conquer Approach} \label{YML and XMP Multi-level Parallelism Programming Paradigm}

\input{Chapter9}

\chapter{Conclusion and Perspectives} \label{Conclusion and Pespectives}

\input{Conclusion}

%\tableofcontents
\clearemptydoublepage

\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{biblio}
\clearemptydoublepage

\appendix
\chapter{Scientific Communication}
%\addcontentsline{toc}{chapter}{Scientific Communication}

\input{Communication}

\clearemptydoublepage

\end{document}